# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].


## R as a calculator

You can use R as a basic **calculator**. 

For example:

```{r, echo=TRUE}
42 + 17 

sqrt(243)

1.56*1233

7.21*8^4
```



For more complicated mathematical operations, it is useful to
store intermediate values in **named variables**.

```{r, echo=TRUE}
x <- (42 + 17)*sqrt(43)
y <- 7.21*8^4 + log(2.34)
z <- x/y
z  ## print out the value of z
```

Here, `x`, `y`, and `z` are examples of **variables**.

The pair of characters `<-` used together is known as the **assignment operator** in **R**.
`x <- 2` assigns the value `2` to the variable `x`.


## Variables in R

